Bayesian Modeling and Test Planning for Multi-phase Reliability Assessment

### 2017-12-14 paperDraft3.tex
fixed plots

\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, fullpage}
\usepackage{array}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{caption}
\usepackage{subcaption}

@@

\title{Bayesian Hierarchical Models for Common Components across Multiple System
Configurations}

\begin{abstract}
    We use a Bayesian hierarchical model to assess the reliability of a family
    of vehicles. The proposed model effectively combines information across
    three phases of testing and across common vehicle components. The analysis
    yields estimates of failure rates across failure modes and vehicles as well
    as an overall estimate of the failure rate for the family of vehicles. We
    are also able to obtain estimates of the Fix Effectiveness Factor (FEF), a
    measure of how well repairs between test phases improve failure rates. In
    addition to using all data to improve on current assessments of reliability
    and reliability growth, we illustrate how to leverage the information
    learned from the three developmental test phases to determine the length of
    testing needed to demonstrate a given reliability threshold in the next
    testing phase.
\end{abstract}

@@

% going to add a table that will have the posterior means and 90% credible
% interval limits
\begin{figure}
  \centering
      \includegraphics[width=8cm, height=6cm]{Boxplots}
  \caption{Comparing EMTF for Different Models}
\end{figure}

@@

\pagebreak

@@

The first check we used to decide between the exponential and Weibull models is
to fit the Weibull model and look at the posterior distributions of the
shape parameters and determine if one is a reasonable value.  Looking at the
plot below from the JLTV data, we see that for the 26 components it appears
that the value of one falls in the extreme tails of the distributions.  This is
our first clue that the exponential model will not be a good fit to this data.

% this plot will be remade without title and smaller xlim
\begin{figure}
  \centering
      \includegraphics[width=6cm, height=5cm]{betaPostPlot}
  \caption{Posterior Plots of Shape Parameter}
\end{figure}

This is not a surprising result, because the exponential model assumes constant
failure rate.  For most vehicle components we would expect the failure rate to
increase as the distance driven grows larger, and this corresponds with a shape
parameter between zero and one.  On the other hand, when the shape parameter is
larger than 1, the failure rate will decrease with time/distance.

Now a more formal diagnostic tool, the Deviance information criterion (DIC).
This is a popular method for comparing the goodness of fit of multiple models.
The DIC method gives a slight penalty for larger numbers of parameters.  The DIC
value is a unitless measure with lower values indicating a better fit to the
data.  In the table below we show the DIC results for the different distribution
and structure combinations, we considered with the JLTV dataset.

% need to recheck these numbers %
\begin{tabular}{|l|l|r|}
\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
\cline{1-3}
Distribution    & Structure & DIC \\
\hline
Exponential   & Common Rate Model                     & 21,264.19             \\
              & Hierarchical Rate Model               & 21,244.47             \\
Weibull       & Common Rate Model                     & 20,658.25             \\
              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
\hline
\end{tabular}

Here we have shown that the hierarchical Weibull model fits the data much better
than the exponential, but in general information criteria comparisons do not
tell us if the model is truely a good representation of the underlying process.
The last method we will present is called posterior predictive checking
~\cite{ref3}. Here we are given important features of the data. In the JLTV case
we were interested in the total failure counts for each phase and the number of
time the miles between failures was less than 140.  We then used the final model
to simulate 5,000 new datasets. We then plot histograms for each of the 8
vehicles for all 3 phases.  In Figure 1 are examples of the histograms produced,
with the line showing where the value of the true dataset fell.  For this method
we don’t expect all of the true values to fall in the center of the
distribution.  Values in the tales are to be expected in a random processes like
this one.  We will only be concerned if we find true values falling in the
extreme tails or if we see a common bias to the high or low side of the
distributions.

% these plots will be redone and I plan to add a contrasting version of them
% using the exponential model
\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{Rplot1}
  \caption{Plot 1}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{Rplot2}
  \caption{Plot 2}
  \label{fig:sub2}
\end{subfigure}
\caption{Posterior Predictive Plots}
\label{fig:test}
\end{figure}

@@

\subsubsection{Classical Approach}
In the frequentist (classical) version we will use two criteria in determining
the test plans. The \emph{producer's risk}, defined as the probability of
failing the test when $\pi = \pi_0$, and the \emph{consumer's risk}, defined as
the probability of passing the test when $\pi = \pi_1$.  Suppose that we specify
a maximum value, $\alpha$, of the producer's risk and a maximum value, $\beta$,
of the consumer's risk. For test planning, these criteria become
$$
\begin{aligned}
	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
\end{aligned}
$$
and
$$
\begin{aligned}
	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
\end{aligned}
$$
To choose a test plan for specified values of $(\alpha, \pi_0, \beta, \pi_1)$,
we assume a distributional form that defines the relationship between the number
of system failyres $W(t)$ and the reliability $\pi$.  Then we can simply find
the combinations of these probabilities by simultaneously solving these two
equations.  In the case where the component failure times are assumed to be
exponentially distributed with rate parameter $\lambda_i$ the failure counts for
each component come from a homogeneous Poisson process $w_i(t) \sim
\text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
\text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
this purely classical approach.

@@

\subsubsection{Weibull Case}
In the exponential case, we defined our quantity of interest that is related to
system reliability at a given time $\pi$ to be equal to the system failure rate
$\lambda_S$.  This distributional assumption gave us a convenient distributional
form for our system failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$
When we assume the miles to failure for each system component follows a Weibull
distribution the system failure counts no longer follow a homogeneous Poisson
process.  When assuming "bad as old" intra-test repairs we do find that the
failure count for a given failure mode does follow a nonhomogeneous Poisson
process, $w(t)_i \sim \text{Poisson}( (\lambda_i t)^{\gamma_i} )$.  In this case
we no longer have a closed form for the system failure rate $\lambda_S = \sum_i
(\lambda_i t)^{\gamma_i}$.  Because of this, using our previous approach leads to
an unpleasant series of integals with parameters in the bounds.  Thankfully we
can once again lean on Monte Carlo integration and the expression for the
posterior producer's risk for the Weibull test plan $(T,c)$ simplifies to
$$
\begin{aligned}
	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &= \frac{\int_{0}^{\infty}
	 \int_{\lambda_0}^{\infty} 1 - exp(- \gamma \lambda_S T^{\gamma})p(\lambda_S)
	 p(\gamma) d\lambda_S d\gamma} {\int_{0}^{\infty} \int_{0}^{\infty} 1 - exp(-
	 \gamma \lambda_S T^{\gamma})p(\lambda_S) p(\gamma) d\lambda_S d\gamma} \\
	 &\approx \frac{\sum_{j = 1}^{N} 1 - exp(-\gamma^{(j)} \lambda_S^{(j)}
	 T^{\gamma^{(j)}}) I(\lambda_S^{(j)} \geq \lambda_0)} {\sum_{j = 1}^{N} 1 -
	 exp(- \gamma^{(j)} \lambda_S^{(j)} T^{\gamma^{(j)}})}
\end{aligned}
$$
\\
Once again set c to be zero and used N posterior draws for both
$\lambda_S^{(j)}$ and $\gamma^{(j)}$

@@

\subsubsection{JLTV Test Plan Results}
The first step in applying this method to our JLTV dataset is defining $\pi_0$,
$\pi_1$, $\alpha$ and $\beta$.  That is the ARL, RRL, acceptable producer risk
and acceptable consumer risk respectively.  With input from subject matter
experts  we will define the producer's target or ARL as the expected number of
failures in the first 140 miles to be less  than 2, and the consumer's minimum
requirements or RRL as the expected number of failures in  the first 80 miles to
greater than 2.  We will use traditional values of 0.1 and 0.05 for $\alpha$ and
$\beta$ respectively, but in practice these values should always be set based on
the true risk tolerances of the consumer and producers.  This gives us the
following probability statements to satisfy when designing the test:
\\
Consumer Risk : $ P(80^\beta (\lambda_S) \geq 2 \; \vert \text{Test Is Passed}) \leq 0.1 $ \\
Producer Risk : $ P(140^\beta (\lambda_S) \leq 2 \; \vert \; \text{Test Is Failed}) \leq 0.05 $

@@

\begin{tabular}{|l|l|r|}
\multicolumn{2}{c}{\textbf{JLTV Test Plan}} \\
\cline{1-2}
Failures Allowed    & Test Miles Required \\
\hline
1   & 5,300      \\
2   & 6,500      \\
3   & 7,800      \\
4   & 11,100     \\
5   & 13,100     \\
\hline
\end{tabular}

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, fullpage}
\usepackage{array}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

%\pdfminorversion=4
% NOTE: To produce unblinded version, replace "0" with "1" below.
\newcommand{\blind}{1}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%

@@

%\bibliographystyle{natbib}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if1\blind
{
\title{Bayesian Modeling and Test Planning for Multi-phase Reliability Assessment}

\author{Kassandra M.\ Fronczyk\\Institute for Defense Analyses\\Alexandria, VA\\\texttt{kfronczy@ida.org} \and
Alyson G.\ Wilson\\North Carolina State University\\Raleigh, NC\\\texttt{agwilso2@ncsu.edu} \and
James F.\ Gilman\\North Carolina State University\\Raleigh, NC\\\texttt{jfgilman@ncsu.edu}
}
\maketitle} \fi

\if0\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Bayesian Modeling and Test Planning for Multi-phase Reliability Assessment}
\end{center}
  \medskip
} \fi

\bigskip

\begin{abstract}
    We use a Bayesian hierarchical model to assess the reliability of the Joint
    Light Tactical Vehicle (JLTV), which is a family of vehicles. The proposed
    model effectively combines information across three phases of testing and
    across common vehicle components. The analysis yields estimates of failure
    rates for specific failure modes and vehicles as well as an overall estimate
    of the failure rate for the family of vehicles. We are also able to obtain
    estimates of how well vehicle modifications between test phases improve
    failure rates. In addition to using all data to improve on current
    assessments of reliability and reliability growth, we illustrate how to
    leverage the information learned from the three phases to determine
    appropriate specifications for subsequent testing that will demonstrate if
    the reliability meets a given reliability threshold.
\end{abstract}

\noindent%
{\it Keywords:}  Assurance Testing, Combining Information, Defense Acquisition, Reliability, Reliability Growth
\vfill

\newpage

@@

% going to add a table that will have the posterior means and 90% credible
% interval limits
\begin{figure}[h]
  \centering
      \includegraphics[width=9cm, height=7cm]{Boxplots}
  \caption{Comparing EMTF for Different Models}
\end{figure}

@@

@@

The first check we used to decide between the exponential and Weibull models is
to fit the Weibull model and look at the posterior distributions of the shape
parameters and determine if one is a reasonable value.  Looking at the plot in
figure 2 below from the Weibull model fit with the JLTV data, we see that one is
not a reasonable value for any of the 20 failure modes.  This is our first clue
that the exponential model will not be a good fit to this data.

\begin{figure}[h]
  \centering
      \includegraphics[width=8cm, height=7cm]{shapePostPlot}
  \caption{Posterior Plots of Shape Parameter}
\end{figure}

This is not a surprising result, because the exponential model assumes constant
failure rate.  For most vehicle failure modes we would expect the failure rate to
increase as the distance driven grows larger, and this corresponds with a shape
parameter between zero and one.  On the other hand, when the shape parameter is
larger than 1, the failure rate will decrease with time/distance.

Now a more formal diagnostic tool, the Deviance information criterion (DIC).
This is a popular method for comparing the goodness of fit of multiple models.
The DIC method gives a slight penalty for larger numbers of parameters.  The DIC
value is a unit-less measure with lower values indicating a better fit to the
data.  In the table below we show the DIC results for the different distribution
and structure combinations, we considered with the JLTV dataset.

% need to recheck these numbers %
\begin{table}[h]
\centering
\begin{tabular}{|l|l|r|}
\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
\cline{1-3}
Distribution    & Structure & DIC \\
\hline
Exponential   & Common Rate Model                     & 21,264.19             \\
              & Hierarchical Rate Model               & 21,244.47             \\
Weibull       & Common Rate Model                     & 20,658.25             \\
              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
\hline
\end{tabular}
\end{table}

Here we have shown that the hierarchical Weibull model fits the data much better
than the exponential, but in general information criteria comparisons do not
tell us if the model is truly a good representation of the underlying process.
The last method we present is called posterior predictive checking ~\cite{ref3}.
Here we are given important features of the data that we would expect to see if
the experiment was repeted.  In the JLTV case one feature we were interested in
was the number of miles between failure observations that were less than 140
miles.  We then used the final models to simulate 5,000 new datasets for
vehicles tested over the same number of miles for each of the three phases. We
then plot the resulting distributions for each of the 8 vehicles for all 3
phases.  In Figure 3 are two examples of the boxplots produced, one from the
exponential model (left) and one from the Weibull model (right), with the dashed
line showing where the value from the observed dataset fell.  For this method we
don’t expect all of the true values to fall in the center of the distribution.
Some values in the tales are to be expected in a random processes like this one,
but when we see many observations in the tails, as we do with the exponential,
we should consider other modeling options.

\begin{figure}[h!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPExpo}
  %\caption{}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPWeibull}
  %\caption{}
  \label{fig:sub2}
\end{subfigure}
\caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
\label{fig:test}
\end{figure}

@@

\subsubsection{Classical Approach}
In the frequentest (classical) version we will use two criteria in determining
the test plans. The \emph{producer's risk}, defined as the probability of
failing the test when $\pi = \pi_0$, and the \emph{consumer's risk}, defined as
the probability of passing the test when $\pi = \pi_1$.  Suppose that we specify
a maximum value, $\alpha$, of the producer's risk and a maximum value, $\beta$,
of the consumer's risk. For test planning, these criteria become
$$
\begin{aligned}
	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
\end{aligned}
$$
and
$$
\begin{aligned}
	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
\end{aligned}
$$
To choose a test plan for specified values of $(\alpha, \pi_0, \beta, \pi_1)$,
we assume a distributional form that defines the relationship between the number
of system failures $W(t)$ and the reliability $\pi$.  Then we can simply find
the combinations of these probabilities by simultaneously solving these two
equations.  In the case where the component failure times are assumed to be
exponentially distributed with rate parameter $\lambda_i$ the failure counts for
each component come from a homogeneous Poisson process $w_i(t) \sim
\text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
\text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
this purely classical approach.

@@

\subsubsection{Weibull Case}
In the exponential case, we defined our quantity of interest that is related to
system reliability at a given time $\pi$ to be equal to the system failure rate
$\lambda_S$.  This distributional assumption gave us a convenient distributional
form for our system failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$
When we assume the miles to failure for each system component follows a Weibull
distribution the system failure counts no longer follow a homogeneous Poisson
process.  When assuming "bad as old" intra-test repairs we do find that the
failure count for a given failure mode does follow a nonhomogeneous Poisson
process, $w(t)_i \sim \text{Poisson}( (\lambda_i t)^{\gamma_i} )$.  In this case
we no longer have a closed form for the system failure rate $\lambda_S = \sum_i
(\lambda_i t)^{\gamma_i}$.  Because of this, using our previous approach leads to
an unpleasant series of integrals with parameters in the bounds.  Thankfully we
can once again lean on Monte Carlo integration and the expression for the
posterior producer's risk for the Weibull test plan $(T,c)$ simplifies to
$$
\begin{aligned}
	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &= \frac{\int_{0}^{\infty}
	 \int_{\lambda_0}^{\infty} 1 - exp(- \gamma \lambda_S T^{\gamma})p(\lambda_S)
	 p(\gamma) d\lambda_S d\gamma} {\int_{0}^{\infty} \int_{0}^{\infty} 1 - exp(-
	 \gamma \lambda_S T^{\gamma})p(\lambda_S) p(\gamma) d\lambda_S d\gamma} \\
	 &\approx \frac{\sum_{j = 1}^{N} 1 - exp(-\gamma^{(j)} \lambda_S^{(j)}
	 T^{\gamma^{(j)}}) I(\lambda_S^{(j)} \geq \lambda_0)} {\sum_{j = 1}^{N} 1 -
	 exp(- \gamma^{(j)} \lambda_S^{(j)} T^{\gamma^{(j)}})}
\end{aligned}
$$
\\
Once again set c to be zero and used N posterior draws for both
$\lambda_S^{(j)}$ and $\gamma^{(j)}$

@@

\subsubsection{JLTV Test Plan Results}
The first step in applying this method to our JLTV dataset is defining $\pi_0$,
$\pi_1$, $\alpha$ and $\beta$.  That is the ARL, RRL, acceptable producer risk
and acceptable consumer risk respectively.  With input from subject matter
experts  we will define the producer's target or ARL as the expected number of
failures in the first 140 miles to be less  than 3, and the consumer's minimum
requirements or RRL as the expected number of failures in  the first 80 miles to
greater than 3.  We will use traditional values of 0.1 and 0.05 for $\alpha$ and
$\beta$ respectively, but in practice these values should always be set based on
the true risk tolerances of the consumer and producers.  This gives us the
following probability statements to satisfy when designing the test:
\\
Consumer Risk : $ P(80^\beta (\lambda_S) \geq 3 \; \vert \text{Test Is Passed}) \leq 0.1 $ \\
Producer Risk : $ P(140^\beta (\lambda_S) \leq 3 \; \vert \; \text{Test Is Failed}) \leq 0.05 $

@@

\begin{table}[h]
\center
\begin{tabular}{|l|l|r|}
\multicolumn{2}{c}{\textbf{JLTV Test Plan}} \\
\cline{1-2}
Failures Allowed    & Test Miles Required \\
\hline
0   & 5,500      \\
1   & 10,100      \\
2   & 17,900      \\
3   & 30,800     \\
4   & 51,200     \\
\hline
\end{tabular}
\end{table}
